Uniformly Ergodic Data-Augmented MCMC for Fitting Stochastic Epidemic Models to Incidence Data

### 2021-11-02 Manuscripts/Article/Article.tex
test

	It is straightforward to show that the Markov chain $\{(\theta^{(m)}, \z^{(m)})\}_m$ is harris ergodic and converges to the target posterior distribution $\pi(\theta, \z|\Y)$. For any $\pi$-integrable function $g$, the estimator
	$$\bar{g}_m := \frac{1}{m} \sum_{i=0}^{m-1} g(\theta^{(m)}, \z^{(m)})$$
	is therefore consistent for $E_\pi g$, regardless of the starting values of the chain. A Markov chain is uniformly ergodic if for some finite $M$ and positive constant $r<1$ the $n$-step transition kernel $P^n$ satisfies
	$$
	\Vert P^n(x,.)-\pi(.)\Vert_{TV} \le M r^n, \forall x \in \chi
	$$
	where $\Vert \mu \Vert_{TV}$ denotes the total variation norm of the measure $\mu$.
	Uniform ergodicity ensures the existence of a Central Limit Theorem for $\bar{g}_m$ whenever $E_\pi |g|^2 < \infty$ (Jones, 2004), that is,
	$$\sqrt{m}(\bar{g}_m - E_\pi g) \Rightarrow N(0, \sigma^2_g)$$
	for any initial distribution for some positive, finite $\sigma^2_g$. Furthermore, uniform ergodicity implies that the batch means and spectral variance estimators of $\sigma^2_g$ are consistent (ref).

>>>>

	It is straightforward to show that the Markov chain $\{(\theta^{(m)}, \z^{(m)})\}_m$ is harris ergodic and converges to the target posterior distribution $\pi(\theta, \z|\Y)$. For any $\pi$-integrable function $g$, the estimator
	$$\bar{g}_m := \frac{1}{m} \sum_{i=0}^{m-1} g(\theta^{(m)}, \z^{(m)})$$
	is therefore consistent for $E_\pi g$, regardless of the starting values of the chain. A Markov chain is uniformly ergodic if for some finite $M$ and positive constant $r<1$ the $n$-step transition kernel $P^n$ satisfies
	$$
	\Vert P^n(x,.)-\pi(.)\Vert_{TV} \le M r^n, \forall x \in \chi
	$$
	where $\Vert \mu \Vert_{TV}$ denotes the total variation norm of the measure $\mu$.
	Uniform ergodicity ensures the existence of a Central Limit Theorem for $\bar{g}_m$ whenever $E_\pi |g|^2 < \infty$ \cite{Jones.2004}, that is,
	$$\sqrt{m}(\bar{g}_m - E_\pi g) \Rightarrow N(0, \sigma^2_g)$$
	for any initial distribution for some positive, finite $\sigma^2_g$. Furthermore, uniform ergodicity implies that the batch means and spectral variance estimators of $\sigma^2_g$ are consistent (ref).
